\documentclass[a4paper,10pt]{article}

\usepackage[left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome}
\usepackage[T1]{fontenc}

% -----------------------
% Links (clean look)
% -----------------------
\hypersetup{
  colorlinks=true,
  urlcolor=blue!60!black,
  linkcolor=blue!60!black
}

% -----------------------
% Section styling + spacing
% -----------------------
\titleformat{\section}
  {\normalfont\Large\bfseries\color{blue!70!black}}{}{0em}{}
\titleformat{\subsection}
  {\normalfont\bfseries\color{blue!70!black}}{}{0em}{}

% Tight, consistent spacing around headings
\titlespacing*{\section}{0pt}{0.7em}{0.35em}
\titlespacing*{\subsection}{0pt}{0.5em}{0.25em}

% -----------------------
% Uniform bullet formatting (circle bullets everywhere)
% -----------------------
\setlist[itemize]{
  label=\textbullet,
  leftmargin=1.25em,
  itemsep=0.15em,
  topsep=0.25em,
  parsep=0em,
  partopsep=0em
}
% Nested itemize (slightly tighter + slightly smaller indent)
\setlist[itemize,2]{
  label=\textbullet,
  leftmargin=1.35em,
  itemsep=0.1em,
  topsep=0.15em
}

% For smaller, gray URLs in header
\newcommand{\printurl}[1]{\textcolor{gray}{\small \texttt{#1}}}

\begin{document}

\begin{center}
    {\LARGE \bfseries Mohammed Abdelazim}\\[2pt]
    Berlin, Germany \quad | \quad \href{mailto:Mohammed@azab.io}{Mohammed@azab.io} \quad | \quad +49 1523 8600805\\[5pt]
    \href{https://linkedin.com/in/mohammed-azab}{LinkedIn:} \printurl{https://linkedin.com/in/mohammed-azab} \quad | \quad
    \href{https://github.com/mohammed-azab}{GitHub:} \printurl{https://github.com/mohammed-azab} \\
    \href{https://mohammedazab.com}{Portfolio:} \printurl{https://mohammedazab.com}
\end{center}

% -----------------------
% Publications
% -----------------------
\section*{Publications}
\begin{itemize}
    \item \textbf{AROLA: A Modular Layered Architecture for Scaled Autonomous Racing}\\
    \textit{IEEE Intelligent Vehicles Symposium (IV26), Detroit, Michigan, USA}
    \begin{itemize}
        \item developed A modular, layered autonomous-driving architecture using ROS 2 to support scalable, reusable racing systems.
        \item Designed a full-stack driving pipeline integrating sensing, perception, localization, planning, behavior, control, and actuation layers.
        \item Developed \textit{Race Monitor}, a real-time evaluation framework, was developed to benchmark controllers in simulation and real-world experiments.
        \item The system facilitated rapid controller comparison, efficient parameter tuning, and reproducible experiments across diverse platforms.
        \item The approach was validated by achieving \textbf{ a 3rd place} finish at RoboRacer IV25 in Cluj, Romania.
    \end{itemize}
\end{itemize}

% -----------------------
% Education
% -----------------------
\section*{Education}
\textbf{Technische Universit채t Berlin} \hfill Berlin, Germany\\
External / Visiting Student, Institute of Elektrotechnik und Informatik \hfill Mar 2026 -- Aug 2026\\
\textbf{Bachelor Thesis:} Comfort-aware preview speed planning and control over speed bumps using LiDAR-based wheel excitation sensing\\

\textbf{German International University in Berlin} \hfill Berlin, Germany\\
B.Sc. in Mechatronics Engineering \hfill Oct 2023 -- Present\\
GPA: \textbf{0.92 (A+)}\\
Relevant Coursework: Autonomous Systems, Control Systems Engineering, Power Electronics, Embedded Systems, Numerical Analysis, Thermodynamics, Fluid Mechanics, Software Engineering.\\

\textbf{The German University in Cairo} \hfill New Cairo, Egypt\\
B.Sc. in General Engineering \hfill Sep 2022 -- Aug 2023\\
GPA: \textbf{0.79 (A+)}\\
Relevant Coursework: Advanced Calculus, Computer Science, Digital Logic Design, Physics III.\\

\subsection*{Honors \& Scholarships}
\begin{itemize}
    \item GUC Scholarship for Outstanding Thanaweya Amma Achievement (2022)
    \item GUC Scholarship for Study Abroad in Germany (2023)
\end{itemize}

% -----------------------
% Research Experience
% -----------------------
\section*{Research Experience}
\textbf{Multi-Robot Systems (MRS) Research Group} \hfill New Cairo, Egypt\\
Research Intern \hfill Aug 2024 -- Oct 2024
\begin{itemize}
    \item Developed a quadrant drone using Embedded C, focusing on control algorithms and flight stability.
    \item Designed and implemented a PID controller in MATLAB/Simulink for precise stabilization.
    \item Reduced drone weight by 23\% using SolidWorks, increasing flight time by 15\%.
\end{itemize}

% -----------------------
% Professional Experience
% -----------------------
\section*{Professional Experience}
\textbf{CARIAD SE -- A Volkswagen Group Company} \hfill Berlin, Germany\\
Working Student -- Software Engineer (ADAS/AD) \hfill May 2025 -- Present
\begin{itemize}
    \item Operate advanced test bench environments to measure and validate sensor data (LiDAR, radar, camera) for Automated Driving Systems.
    \item Develop, debug, and optimize test and measurement tools using C++ and Python on Ubuntu.
    \item Work with CI pipelines, CMake, and Conan for scalable build automation and dependency management.
    \item Author comprehensive technical documentation, ensuring clarity and traceability of test procedures.
\end{itemize}

% -----------------------
% Projects
% -----------------------
\section*{Projects}
\textbf{F1TENTH Autonomous Racing Car}
\begin{itemize}
    \item Built a 1/10th scale autonomous race car on the F1TENTH platform, running ROS2 on NVIDIA Jetson.
    \item Implemented SLAM for real-time mapping and localization.
    \item Developed a Bezier spline-based path optimizer and \textbf{hybrid MPC--LQR controller} for trajectory planning.
    \item Implemented a dual Extended Kalman Filter (EKF) to fuse control inputs, IMU, and odometry data for accurate state estimation.
    \item Achieved \textbf{3rd place} in the 25th RoboRacer Autonomous Racing Competition, Romania.
\end{itemize}

\textbf{TriFlameX: Swarm of Fire-Fighting Robots}
\begin{itemize}
    \item Developed 3 autonomous robots with multi-layer architecture (Laptop--ESP32--STM32) for coordinated detection and suppression of fires.
    \item Invented the interrupt-driven Azab Protocol for high-speed reliable binary communication in FreeRTOS.
    \item Designed a custom thermal LiDAR system for real-time fire localization.
    \item Integrated ROS2, MQTT, and UART for inter-robot and intra-robot communication.
\end{itemize}

\textbf{Dice Realms: Quest for the Elemental Crests}
\begin{itemize}
    \item Developed a 2D board game in Java, with object-oriented programming (OOP) architecture.
    \item Implemented a finite state machine (FSM) to manage structured game flow and modular code architecture.
    \item Developed AI players using a Monte Carlo method for decision-making, supporting multiple difficulty levels and both human vs AI and AI vs AI gameplay.
    \item Designed UI in JavaFX and CSS; implemented version control with Git and GitHub.
\end{itemize}

\textbf{Thyristor-Based Battery Charger Modeling and Rectifier Analysis}
\begin{itemize}
    \item Developed a MATLAB and Simulink toolkit for analyzing thyristor-controlled rectifiers and optimizing battery charging profiles.
    \item Simulatied models for half-wave, full-wave center-tapped, and bridge rectifiers with adjustable firing angle control.
    \item Performed waveform analysis, power loss evaluation, and state-of-charge tracking for R, RL, and highly inductive loads using Simscape Electrical.
\end{itemize}

% -----------------------
% Skills
% -----------------------
\section*{Skills}
\textbf{Technical:} System Optimization, Hardware-Software Integration, API Documentation\\
\textbf{Programming:} Embedded C, C++, Java, Python, VHDL, Assembly, CSS\\
\textbf{Operating Systems:} Ubuntu, Arch Linux, Windows\\
\textbf{Tools:} ROS2, Git, MATLAB/Simulink, Quartus, Gazebo, Bash, PowerShell\\
\textbf{Hardware Platforms:} Raspberry Pi, NVIDIA Jetson, STM32, ESP32, Arduino, FPGA\\
\textbf{Languages:} English (C1), German (B2), Arabic (Native)\\
\textbf{Interpersonal:} Public Speaking, Leadership, Communication, Time Management

% -----------------------
% Certifications
% -----------------------
\section*{Certifications \& Courses}
\begin{itemize}
    \item Robotics \& Automation: ROS 2 Humble
    \item Machine Learning (DeepLearning.AI): Supervised \& Unsupervised Learning, Recommenders, Reinforcement Learning, Advanced Algorithms
    \item Digitalization in the Aerospace Industry, Technische Universit채t M체nchen
    \item Mechanical Design: Siemens NX, Fusion 360, SolidWorks, AutoCAD
    \item Programming \& Operation of 5-Axis CNC Machines
    \item Goethe-Zertifikat B2 (German)
\end{itemize}

% -----------------------
% Leadership
% -----------------------
\section*{Leadership \& Activities}
\textbf{European Solidarity Corps for Youth (ESC4Y)} \hfill Deuselbach, Germany\\
Biodiversity and Climate Action Volunteer \hfill Sep 2024 -- Oct 2024
\begin{itemize}
    \item Collaborated with IBG and the Foundation for Nature and Environment to support biodiversity (UN SDG 15) and climate action (UN SDG 13).
    \item Assisted park rangers in restoring peatlands in Hunsr체ck-Hochwald National Park.
\end{itemize}

\end{document}
