\documentclass[a4paper,10pt]{article}
\usepackage[left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome}

% Modern section style
\titleformat{\section}
  {\normalfont\Large\bfseries\color{blue!70!black}}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\bfseries\color{blue!70!black}}{\thesubsection}{1em}{}

% For smaller, gray URLs in header
\newcommand{\printurl}[1]{\textcolor{gray}{\small \texttt{#1}}}

\begin{document}

\begin{center}
    {\LARGE \bfseries Mohammed Abdelazim}\\[2pt]
    Berlin, Germany \quad | \quad \href{mailto:Mohammed@azab.io}{Mohammed@azab.io} \quad | \quad +49 1523 8600805\\[6pt]
    \href{https://linkedin.com/in/mohammed-azab}{LinkedIn:} \printurl{https://linkedin.com/in/mohammed-azab} \quad | \quad
    \href{https://github.com/mohammed-azab}{GitHub:} \printurl{https://github.com/mohammed-azab} \\
    \href{https://mohammedazab.com}{Portfolio:} \printurl{https://mohammedazab.com}\\
\end{center}

\vspace{0.6em}

\section*{Education}
\textbf{German International University in Berlin} \hfill Berlin, Germany\\
B.Sc. in Mechatronics Engineering \hfill Oct 2023 -- Present\\
GPA: \textbf{0.81 (A+)}\\
Relevant Coursework: Autonomous Systems, Control Systems Engineering, Power Electronics, Embedded Systems, Numerical Analysis, Thermodynamics, Fluid Mechanics, Software Engineering.\\

\textbf{The German University in Cairo} \hfill New Cairo, Egypt\\
B.Sc. in General Engineering \hfill Sep 2022 -- Aug 2023\\
GPA: \textbf{0.79 (A+)}\\
Relevant Coursework: Advanced Calculus, Computer Science, Digital Logic Design, Physics III.\\

\subsection*{Honors \& Scholarships}
\begin{itemize}[noitemsep,topsep=0pt]
    \item GUC Scholarship for Outstanding Thanaweya Amma Achievement (2022)
    \item GUC Scholarship for Study Abroad in Germany (2023)
\end{itemize}

\vspace{0.6em}

\section*{Research Experience}
\textbf{Multi-Robot Systems (MRS) Research Group} \hfill New Cairo, Egypt\\
Research Intern \hfill Aug 2024 -- Oct 2024
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed a quadrant drone using Embedded C, focusing on control algorithms and flight stability.
    \item Designed and implemented a PID controller in MATLAB/Simulink for precise stabilization.
    \item Reduced drone weight by 23\% using SolidWorks, increasing flight time by 15\%.
\end{itemize}

\vspace{0.6em}

\section*{Professional Experience}
\textbf{CARIAD SE – A Volkswagen Group Company} \hfill Berlin, Germany\\
Working Student – Test \& Measurement Engineer (ADAS/AD) \hfill May 2025 -- Present
\begin{itemize}[noitemsep,topsep=0pt]
    \item Operate advanced test bench environments to measure and validate sensor data (LiDAR, radar, camera) for Automated Driving Systems.
    \item Develop, debug, and optimize test and measurement tools using C++ and Python on Ubuntu.
    \item Work with CI pipelines, CMake, and Conan for scalable build automation and dependency management.
    \item Author comprehensive technical documentation, ensuring clarity and traceability of test procedures.
\end{itemize}

\vspace{0.6em}

\section*{Projects}
\textbf{F1TENTH Autonomous Racing Car}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Built a 1/10th scale autonomous race car on the F1TENTH platform, running ROS2 on NVIDIA Jetson.
    \item Implemented SLAM for real-time mapping and localization.
    \item Developed a Bezier spline-based path optimizer and hybrid MPC–LQR controller for trajectory planning.
    \item Implemented a dual Extended Kalman Filter (EKF) to fuse control inputs, IMU, and odometry data for accurate state estimation.
    \item Achieved 3rd place in the 25th RoboRacer Autonomous Racing Competition, Romania.
\end{itemize}

\textbf{TriFlameX: Swarm of Fire-Fighting Robots}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed 3 autonomous robots with multi-layer architecture (Laptop–ESP32–STM32) for coordinated detection and suppression of fires.
    \item Invented the interrupt-driven Azab Protocol for high-speed reliable binary communication in FreeRTOS.
    \item Designed a custom thermal LiDAR system for real-time fire localization.
    \item Integrated ROS2, MQTT, and UART for inter-robot and intra-robot communication.
\end{itemize}

\textbf{Dice Realms: Quest for the Elemental Crests}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed a 2D board game in Java, with object-oriented programming (OOP) architecture.
    \item Implemented a finite state machine (FSM) to manage structured game flow and modular code architecture.
    \item Developed AI players using a Monte Carlo method for decision-making, supporting multiple difficulty levels and both human vs AI and AI vs AI gameplay.
    \item Designed UI in JavaFX and CSS; implemented version control with Git and GitHub.
\end{itemize}

\textbf{FPGA Edge Detection}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Designed a real-time edge detection algorithm using VHDL on FPGA using the Prewitt filter method.
    \item Applied matrix theory for adaptive thresholds, improving detection accuracy.
    \item Validated performance using Altera tools and custom testbench.
\end{itemize}

\vspace{0.6em}

\section*{Skills}
\textbf{Technical:} System Optimization, Hardware-Software Integration, API Documentation\\
\textbf{Programming:} Embedded C, C++, Java, Python, VHDL, Assembly, CSS\\
\textbf{Operating Systems:} Ubuntu, Arch Linux, Windows\\
\textbf{Tools:} ROS2, Git, MATLAB/Simulink, Quartus, Gazebo, Bash, PowerShell\\
\textbf{Hardware Platforms:} Raspberry Pi, NVIDIA Jetson, STM32, ESP32, Arduino, FPGA\\
\textbf{Languages:} English (C1), German (B2), Arabic (Native)\\
\textbf{Interpersonal:} Public Speaking, Leadership, Communication, Time Management

\vspace{0.6em}

\section*{Certifications \& Courses}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Robotics \& Automation: ROS 2 Humble
    \item Machine Learning (DeepLearning.AI): Supervised \& Unsupervised Learning, Recommenders, Reinforcement Learning, Advanced Algorithms
    \item Digitalization in the Aerospace Industry, Technische Universität München
    \item Mechanical Design: Siemens NX, Fusion 360, SolidWorks, AutoCAD
    \item Programming \& Operation of 5-Axis CNC Machines
    \item Goethe-Zertifikat B2 (German)
\end{itemize}

\vspace{0.6em}

\section*{Leadership \& Activities}
\textbf{European Solidarity Corps for Youth (ESC4Y)} \hfill Deuselbach, Germany\\
Biodiversity and Climate Action Volunteer \hfill Sep 2024 -- Oct 2024
\begin{itemize}[noitemsep,topsep=0pt]
    \item Collaborated with IBG and the Foundation for Nature and Environment to support biodiversity (UN SDG 15) and climate action (UN SDG 13).
    \item Assisted park rangers in restoring peatlands in Hunsrück-Hochwald National Park.
\end{itemize}

\vspace{0.6em}

% Publications section (leave blank if none, but ready for future updates)
\section*{Publications}
\textit{Currently no formal publications.}

\end{document}